%!TEX TS-program = xelatex
%!TEX root = ../maxwell2018thesis.tex

% To refer to a glossary entry, use the \gls{} command.
% If there is an acronym for the glossary entry, refer to the acronym, which in turn cross-references the glossary entry.

% To add a new glossary entry, use the following template.
%
% \newglossaryentry{glos:NAME}{
%     name={GLOSSARY ENTRY},
%     description={DESCRIPTION},
%     first={\emph{FIRST MENTION}},
% }
%
% Note that first won't be used when the acronym is used.


\newglossaryentry{glos:ir}{
    name={IR},
    description={As a field of academic study, \emph{Information Retrieval} could be defined as the study of \emph{``finding material (usually documents) of an unstructured nature (usually text) that satisfies an information need from within large collections (usually stored on computers)''}~\citep{manning2008ir}.},
}

\newglossaryentry{glos:qrel}{
    name={QREL},
    text={QREL},
    plural={QRELs},
    description={\emph{Query RElevance Judgements} are a series of judgements that are assigned to documents within a corpus. Typically, these are considered over a per-topic basis, with \emph{binary} or \emph{graded} judgements assigned. As an example, binary judgements would denote that some item is either \emph{relevant} and \emph{not relevant.} These are considered as the ground truth or gold standard judgements of relevance.},
}

\newglossaryentry{glos:info_need}{
    name={Information Need},
    text={information need},
    plural={information needs},
    description={A searcher can develop an \emph{information need} when observing some phenomenon in the real world. It is a desire to locate and obtain information to satisfy a conscious or unconscious need. This is typically considered to be one of the first steps of the~\gls{acr:iir} process.},
}

\newglossaryentry{glos:ip}{
    name={iP},
    description={Similar to~\gls{glos:precision}, \emph{interactive precision} considers the fraction of relevant documents relevant to the issued query, as identified \emph{by the searcher.}},
}

\newglossaryentry{glos:ar}{
    name={AR},
    description={\emph{Aspectual Recall} considers the number of documents returned by a retrieval system that reference at least one unseen \emph{aspect} of a particular topic. An interactive-based approach can also be considered, where documents identified by searchers are exclusively considered.},
}

\newglossaryentry{glos:mse}{
    name={MSE},
    description={The \emph{Mean Squared Error} measures the average squared difference between estimated values, and what is being estimated. It considers the notion of bias and standard error, with the lower the MSE, the better the estimation to the real-world observation.},
}

\newglossaryentry{glos:query}{
    name={Query},
    text={query},
    plural={queries},
    description={A \emph{query} is a precise request issued to a retrieval system. Here, a searcher's \emph{information need} is formulated as one or more \emph{query terms.}},
}

\newglossaryentry{glos:summary}{
    name={Result Summary},
    text={result summary},
    plural={result summaries},
    description={On a~\gls{acr:serp}, a \emph{result summary} provides a title, summary and source for a document that was matched to the searcher's query. Result summaries are the \emph{ten blue links} one is accustomed to when interacting with a retrieval system.},
}

\newglossaryentry{glos:recall}{
    name={Recall},
    text={recall},
    description={\emph{Recall} denotes the number of relevant documents that were matched against a searcher's query by a given retrieval system.},
}

\newglossaryentry{glos:summary_stopping}{
    name={Result Summary Level Stopping},
    text={result summary level stopping},
    description={In this thesis, \emph{result summary level stopping} denotes the~\gls{glos:stopping_decision_point} when a searcher is interacting with a~\gls{acr:serp}. It considers the \emph{depth} to which a searcher will examine~\glsplural{glos:summary}. This is typically referred to as \emph{snippet level} or \emph{query level stopping} in the literature.},
}

\newglossaryentry{glos:serp_stopping}{
    name={SERP Level Stopping},
    text={SERP level stopping},
    description={\emph{\gls{acr:serp} level stopping} denotes the~\gls{glos:stopping_decision_point} where a searcher can choose to either \emph{enter} a~\gls{acr:serp} and begin examining content in detail, or \emph{abandon} the~\gls{acr:serp} and move on to the next action.},
}

\newglossaryentry{glos:session_stopping}{
    name={Session Level Stopping},
    text={session level stopping},
    description={\emph{Session level stopping} considers stopping in terms of the overall search session. Typically, this would be evaluated in consideration of time limits or search session goals (i.e. find $x$ relevant documents).},
}

\newglossaryentry{glos:iir}{
    name={IIR},
    description={A simplistic description of \emph{Interactive Information Retrieval} would be the study of how humans interact with retrieval systems, considering aspects such as their behaviours and experiences. This is in contrast to the study of~\gls{acr:ir}, considering purely \emph{system-sided} aspects.},
}

\newglossaryentry{glos:www}{
    name={WWW},
    description={The \emph{World Wide Web} is an information space in which documents and other resources, linked together via~\glsplural{glos:hyperlink}, can be accessed via the~\gls{glos:internet}.},
}

\newglossaryentry{glos:kl}{
    name={KL-Divergence},
    text={KL-divergence},
    first={\emph{Kullback–Leibler Divergence}},
    description={\emph{Kullback-Leibler} divergence, or \emph{relative entropy}, is a measure of how one probability distribution is different from a second.}
}

\newglossaryentry{glos:precision}{
    name={Precision},
    text={precision},
    description={The fraction of documents retrieved that are relevant to the searcher's query. This is typically presented as $P@k$ or the fraction of relevant documents up to some rank $k$.},
}

\newglossaryentry{glos:serp}{
    name={SERP},
    first={SERP},
    description={A Search Engine Results Page is the primary output of a contemporary retrieval system (typically WWW-based). It is a page consisting of a series of results that were matched by the retrieval system to the searcher's \emph{query.}},
}

\newglossaryentry{glos:univac}{
    name={UNIVAC},
    first={UNIVAC},
    description={The \emph{Universal Automatic Computer}, one of the first electronic, stored-program computers utilised to execute what is considered to be a~\gls{glos:ir} system.},
}

\newglossaryentry{glos:html}{
    name={HTML},
    first={HTML},
    description={\emph{HyperText Markup Language} is the standard \emph{markup language} used in the development of web pages and web applications. HTML documents are annotated in a way that is syntactically different from the text, such as through the use of \texttt{<tags>}).},
}

\newglossaryentry{glos:rdbms}{
    name={RDBMS},
    first={RDBMS},
    description={A \emph{Relational DataBase Management System} is a type of database management system based upon the relational model. At a minimum, a RDBMS provides data as a series of \emph{tables,} comprised of rows and columns, and the ability to create \emph{relationships} between the said tables and data.},
}

\newglossaryentry{glos:trec}{
    name={TREC},
    first={TREC},
    description={The \emph{Text REtrieval Conference} is an~\gls{acr:ir} evaluation forum, considering a number of different research areas, or \emph{tracks.} Central to the TREC effort is the development of topics, tasks and document collections \emph{(corpora)} that are commonly used in~\gls{acr:ir} experimentation -- with this thesis included.},
}

\newglossaryentry{glos:hci}{
    name={HCI},
    first={HCI},
    description={Human-Computer Interaction is the study of how computer technology is used and designed. It focuses on the interfaces between users and computers.},
}

\newglossaryentry{glos:cg}{
    name={CG},
    first={CG},
    description={\emph{Cumulative Gain} is used to measure the effectiveness of a retrieval system (or the searchers that use it). The usefulness or \emph{gain} possessed by each ranked document is considered and accumulated together to produce a final measure. This can be at the \emph{query level} (i.e. considering individual queries), or at the \emph{session level} (considering the total gain acquired over a number of queries).},
}

\newglossaryentry{glos:dcg}{
    name={DCG},
    first={DCG},
    description={Considered as a natural evolution of~\gls{glos:cg}, \emph{Discounted Cumulative Gain} once again considers the \emph{gain} that can be attained from a document. However, the underlying assumption here is that relevant documents at higher ranks are more desirable. Gain therefore for documents at lower ranks are \emph{penalised,} or discounted, producing a rank-aware measure.},
}

\newglossaryentry{glos:rbp}{
    name={RBP},
    first={RBP},
    description={\emph{Rank-Biased Precision}~\citep{moffat2008rbp} is an evaluation measure used within~\gls{acr:ir}. It encodes within it a simple model of searcher behaviour, with a \emph{patience} factor denoting how far down a list of ranked results a searcher is prepared to go.},
}

\newglossaryentry{glos:ift}{
    name={IFT},
    first={IFT},
    description={\emph{Information Foraging Theory} applies the theory and constructs provided as part of~\gls{glos:oft}. First considered in the 1990s with seminal work by~\cite{pirolli1999ift}, IFT considers~\glsplural{glos:searcher} as individuals when searching for information. This analogy allows one to consider how instinctive foraging mechanisms employed by animals looking for food in the wild can be applied to humans when \emph{foraging for information}.},
}

\newglossaryentry{glos:csm}{
    name={CSM},
    first={CSM},
    description={The \emph{Complex Searcher Model} is the high-level, conceptual searcher model proposed in this thesis. It is a development of existing searcher models provided in the associated literature. The model considers the search session as a whole and incorporates novel improvements to the search process, such as a new \emph{stopping decision point.}},
}

\newglossaryentry{glos:url}{
    name={URL},
    first={URL},
    plural={URLs},
    description={A \emph{Uniform Resource Locator} is a reference to some resource hosted on a computer network. It contains the address to the resource and the means by which it can be retrieved. For example, the URL \texttt{http://www.dmax.org.uk} specifies that HTTP is used to retrieve content at the address \texttt{www.dmax.org.uk}.},
}

\newglossaryentry{glos:fqdn}{
    name={FQDN},
    first={FQDN},
    plural={FQDNs},
    description={A \emph{Fully Qualified Domain Name} is a domain that specifies a host's exact location within a domain name hierarchy. For example, \texttt{www} may be a valid hostname, but \texttt{www.gla.ac.uk} provides an exact match to the host's location within a wider network.},
}

\newglossaryentry{glos:http}{
    name={HTTP},
    first={HTTP},
    description={The \emph{HyperText Transfer Protocol} is the underlying protocol used for the transmission of content over the~\gls{glos:www}, amongst many other protocols. It defines the rules by which web servers and web browsers can communicate with one another.},
}

\newglossaryentry{glos:hyperlink}{
    name={Hyperlink},
    text={hyperlink},
    first={\emph{hyperlink}},
    firstplural={\emph{hyperlinks}},
    plural={hyperlinks},
    description={A \emph{hyperlink} is a reference to some data source that can be clicked on to jump to the said data source. This concept is most well known as part of the~\gls{glos:www}, with the links that hyperlinks create between documents defining the web-like structure.}
}

\newglossaryentry{glos:internet}{
    name={Internet},
    first={\emph{Internet}},
    description={The \emph{Internet} is a global system of interconnected computer networks. This \emph{network of networks} consists of private, public, business, governmental and academic computer networks all working together to provide \emph{routes} to computers, or hosts, all over the world.}
}

\newglossaryentry{glos:nist}{
    name={NIST},
    first={NIST},
    description={The \emph{National Institute for Standards and Technology} is a laboratory and non-regulatory agency of the \emph{U.S. Department of Commerce.} NIST has been central in providing support to the~\gls{acr:trec} evaluation effort.}
}

\newglossaryentry{glos:mturk}{
    name={MTurk},
    first={MTurk},
    description={\emph{Amazon Mechanical Turk} is a \emph{crowdsourcing} platform, allowing for one to coordinate the use of human intelligence to perform tasks that computers cannot presently do.}
}

\newglossaryentry{glos:set}{
    name={SET},
    first={SET},
    description={\emph{Search Economic Theory}~\citep{azzopardi2011economics} is a theory explaining the search process in terms of economics -- in particular \emph{microeconomic theory}. Under this approach, the search process is viewed as a series of \emph{inputs (queries, assessments)} that are used to produce an \emph{output (relevance).}}
}

\newglossaryentry{glos:esl}{
    name={ESL},
    first={ESL},
    description={The \emph{Expected Search Length} is an evaluation measure used within~\gls{acr:ir}. It considers the number of non-relevant documents that will have to be examined by a searcher before reaching the desired number of relevant documents. The ESL provides motivation for a number of~\glsplural{glos:stopping_heuristic} used within this thesis.}
}

\newglossaryentry{glos:oft}{
    name={OFT},
    first={OFT},
    description={\emph{Optimal Foraging Theory}~\citep{stephens1986foraging_theory} is a behavioural ecology model that helps to predict how animals behave when searching for food. An optimal foraging strategy is employed that provides the most gain (energy) at the lowest cost.}
}

\newglossaryentry{glos:mvt}{
    name={MVT},
    first={MVT},
    description={The \emph{Marginal Value Theorem}~\citep{charnov1976mvt} is an optimisation model used to describe the behaviour of individuals foraging in a system where resources are located in discrete~\glsplural{glos:patch}.}
}

\newglossaryentry{glos:stopping_heuristic}{
    name={Stopping Heuristic},
    text={stopping heuristic},
    plural={stopping heuristics},
    firstplural={stopping heuristics},
    description={A \emph{stopping heuristic} is defined in this thesis as a heuristic that describes the stopping behaviour of a searcher. A heuristic may consider one or more \emph{stopping criteria} when determining a stopping point.}
}

\newglossaryentry{glos:stopping_strategy}{
    name={Stopping Strategy},
    text={stopping strategy},
    plural={stopping strategies},
    firstplural={stopping strategies},
    description={A \emph{stopping strategy} is an operationalised~\gls{glos:stopping_heuristic}. The heuristic is converted to a series of rules that can be subsequently operationalised -- and later implemented -- as part of a wider searcher model.}
}

\newglossaryentry{glos:stopping_decision_point}{
    name={Stopping Decision Point},
    text={stopping decision point},
    plural={stopping decision points},
    description={Core to this thesis, we refer to \emph{stopping decision points} as the decision points within the~\gls{acr:csm} that permit a searcher to stop their current activity (i.e. examining result summaries or the search session).}
}

\newglossaryentry{glos:prp}{
    name={PRP},
    first={PRP},
    description={The \emph{Probability Ranking Principle}~\citep{cooper1971relevance, robertson1977prp} is a fundamental theory of~\gls{acr:ir}, outlining that for a retrieval system to be effective, it must present results to a searcher in decreasing order of likelihood of the results being relevant.}
}

\newglossaryentry{glos:iprp}{
    name={iPRP},
    first={iPRP},
    description={The \emph{Interactive Probability Ranking Principle}~\citep{fuhr2008iprp} is an update to the~\gls{glos:prp}. It considers interaction within its framework, allowing for costs over different activities (i.e. issuing queries, examining documents) and changes in a searcher's information need.}
}

\newglossaryentry{glos:searcher}{
    name={Searcher},
    text={searcher},
    plural={searchers},
    description={A \emph{searcher} is an individual who uses a retrieval system to help him or her satisfy some given~\gls{glos:info_need}.}
}

\newglossaryentry{glos:user}{
    name={User},
    text={user},
    plural={users},
    description={Analagous to a \emph{\gls{glos:searcher}}.}
}

\newglossaryentry{glos:patch}{
    name={Patch},
    text={patch},
    plural={patches},
    description={Considering~\gls{acr:oft}, a \emph{patch} is considered an area a forager's surrounding environment. In each patch, the forager can extract gain. Using the example by~\cite{pirolli1999ift}, a bird foraging for berries would find berries on different berry bushes. Each bush can be considered an individual patch with different levels of gain. The bird would expend time on a particular bush (within-patch) and then fly to the next patch (between-patch). Under~\gls{acr:ift}, a patch is typically considered as a~\gls{acr:serp}.}}

\newglossaryentry{glos:hit}{
    name={HIT},
    text={HIT},
    description={A \emph{Human Intelligence Task} is the name given to jobs posted on the~\gls{acr:mturk} platform.}
}

\newglossaryentry{glos:document}{
    name={Document},
    text={document},
    plural={documents},
    description={In an~\gls{acr:ir} system, a \emph{document} contains information that can be examined. Typically, this would consist of unstructured text (i.e. natural language). However, depending upon the context, a document may contain other forms of information, such as images, audio, or video.}
}