%!TEX TS-program = xelatex
%!TEX root = ../../maxwell2018thesis.tex

\begin{preamble}[Acknowledgements and Reflections]
\phantomsection
\addcontentsline{toc}{part}{Acknowledgements and Reflections}

\todo{Anastasia, Helen McNeee, Autumn School (ASIRF), MUMIA (Tampere, Summer School), SoCS RSC Funding,...}

A good friend of mine -- and a fellow PhD student -- once said to me that when the time came to write his PhD thesis, he would avoid an acknowledgements section where \emph{everyone and their dog} would be thanked for being part of his life. I on the other hand take a very different light on this matter; there are a lot of people who have helped me get to where I am today in some form. \textbf{\emph{To show my appreciation, I want to dedicate this work to each and every one of them}} -- regardless of whether they have a dog or not.

So, where do I begin? I guess day one of the PhD is a good place to start -- October 1\textsuperscript{st}, 2013. Sitting in my new office with (relatively) new faces around me, I remember thinking something along the lines of \emph{what have I just let myself in for?} But despite the occasional set of disappointing results, the existential questioning of \emph{what am I doing}, along with the challenges I've faced outside my PhD, I've got through to the other side complete with a much better understanding of my subject and life in general -- as well as countless good memories to go with all of that. I did not for one minute think that within the intermediary four years, I would drive along the Pacific Highway in New South Wales, wander the streets of New York City with my friend Hora\c{t}iu, or have drinks with my friend Jarana in downtown Tokyo. During my PhD, I have been incredibly fortunate to undertake interesting experiments (that \emph{did} work), and as a perk of getting them published, travel the world. And in doing so, I have met some amazing people with whom I have had the opportunity to share what I have been working on -- and indeed, learn from. As Professor Ian Ruthven pointed out in his own 2001 thesis, there may only be one name on the front page of a PhD, but countless numbers of people behind the scenes who were involved in the making of it, \emph{``cajoling''} the author (as Ian put it) towards the finishing line.

To the people in \emph{SAWB} Rooms 220 and 221 -- my friends, Colin Wilkie, Jarana Manotumruksa, Stuart Mackie, Stewart Whiting, Fatma Elsafoury, David Paule, James McMinn, Xi Yang, Rami Alkhawaldeh, Fajie Yuan, Phil McParlane, Jesus Perez and his brother Felix, and Shawki Al-Dubaee. Thank you all for your friendship and the good times we have shared. Thank you also to Frances Cooper, G\"{o}zel Shakeri, Craig Reilly, James Trimble, Blair Archibald, Laura Voinea and Natascha Harth for your friendship. To Sean McKeown, it has been an absolute pleasure -- and I know you are doing Edinburgh Napier proud. Most of all though, my thanks to Hora\c{t}iu Bota for your continued friendship as we progressed through our respective PhDs -- \emph{we made it!}

To the Head of School, Professor Chris Johnson -- and Dr. Simon Rogers -- thank you both for the support and trust you bestowed upon me throughout my PhD. To Dr. Yashar Moshfeghi, thank you for your friendship, wisdom and advice throughout the years -- even as my tutor when I was a second year undergraduate! To Professor Rod Murray-Smith, thank you for your feedback and assistance in shaping this thesis into what it is now. Your support after Leif moved to the University of Strathclyde was invaluable. To Helen Border, Gail Reat and Teresa Bonner in the teaching office, I am so glad I could help out with my tutoring and exam collection efforts throughout the years. I enjoyed every second of my tutoring jobs -- I hope that over the eight years I tutored, I got \emph{something} through to a student who was struggling. Indeed, thank you to everyone else in the School of Computing Science who made my time there such an enjoyable and rewarding experience.

To those in the College of Science and Engineering -- especially Heather Lambie -- thank you for letting me disappear several times to go do internships elsewhere. I know it is a pain seeing students disappear for months at a time, so it makes me appreciate your efforts even more. Generally, thank you to the University of Glasgow for providing me with the opportunity to show the world what I can do, and to the \emph{EPSRC} for providing me with a PhD scholarship to get this work done without any financial headaches.\footnote{I acknowledge the financial support offered by the UK Government (through the EPSRC), under grant number \texttt{1367507}.}

To my PhD examiners -- both my internal examiner, \todo{Dr. Some Guy}, and my external examiner, \todo{Dr. Another Guy} at \todo{Some University, Some Country}. I know just how much effort you both put into reading this thesis, and I hope I was able to provide you with the clarity, detail and presentation that you both expected. Thanks to you both for the work you put into assessing this thesis. My thanks also goes to my viva convenor, \todo{Dr. Convenor Person}, for the time and effort in ensuring the examination process was swift and (relatively) painless.

In September 2014, I spent several weeks in Tampere, Finland. Here, I had the opportunity to work with world leaders regarding user modelling and simulation of the Interactive Information Retrieval process. Thank you to Professor Kalervo J\"{a}rvelin, Dr. Jaana Kek\"{a}l\"{a}inen, Dr. Heikki Keskustalo, Teemu P\"{a}\"{a}kk\"{o}nen and Dr. Feza Baskaya for a fantastic, rewarding and memorable time. I learnt so much from you all, and this reflected in the simulation software that was developed during my PhD -- including use of your prototypical querying strategies.

To my good friends Vu Tran and Ioannis Karatassis, thanks for the wonderful time I spent at the University of Duisburg-Essen in Germany in late November to early December 2015. Thank you also to Professor Norbert Fuhr for allowing me to visit, for his counsel, and allowing me to participate on developing the interesting work that we were able to present at the third \emph{International Conference on the Theory of Information Retrieval} in Amsterdam.

To Professor Jaap Kamps at the University of Amsterdam -- thank you for your Doctoral Consortium mentorship at the first \emph{Conference on Human Information Interaction and Retrieval} in North Carolina. The feedback you provided on my work allowed me to formulate some new ideas which subsequently made it into this thesis.

To Johanne and Penny, thank you both for everything you did for me when I visited in Melbourne. To Mostafa and Samira, thank you both for everything you did for me when I visited in Amsterdam. Mostafa, the moped ride from Sloterdijk station was \emph{awesome!} The kindness you all showed me was very much appreciated, and I am happy to repay this at any time.

My thanks also to Dr. Peter Bailey, Dr. Paul Thomas and Professor Dave Hawking for the memorable time at Microsoft Australia. The kindness and support shown by you all was very much appreciated. I learnt so much from my time there -- and this has undoubtedly equipped me to become a better scientist. Thank you so much. To Gabrielle, James, Alan and Az -- it was a pleasure to meet you all, and thank you for your continued friendships. I have nothing but fond memories of my times in Canberra.

I was also fortunate enough to become an intern at the \emph{Alan Turing Institute} in London, during the Summer of 2017. While this internship was not directly applicable to my PhD (nor was my time at Microsoft, for that matter), I did learn lots about a new area -- and of course, had the opportunity to meet and work with some wonderful people. To Emily Neilson, Professor Terry Lyons, Dr. Hao Ni, Dr. Jeremy Reizenstein, Alexandru Cioba, Rados\l{}aw Kowalski, Tim King, James Bell, Haichen Shi and William Kayat  -- to name but a few -- thank you for your friendship and support throughout my time as an intern, and to the Alan Turing Institute for a wonderful experience. Indeed, the Institute is fantastic place to work, with so many bright minds working together. I hope to be able to visit again in the future.

To my mother, Denise, my father, William, and my brother, Alastair -- thank you all for your unwavering support, love and encouragement. It was tough at times. But all three of you were always there for me. I am so happy I have been able to do you all proud. \emph{There is another doctor in the family, now!} To Ian Phillips -- you were the person who taught me everything I needed to know about computing at Standard Grade and Advanced Higher.\footnote{Standard Grades and Advanced Highers were the Scottish qualifications that you obtained from school and/or college, although it seems as though everything has changed since I was a high school student.} As my high school teacher, you were one of the people most conducive in helping me get to where I am today. Thank you so much for everything you did for me at Mearns Castle High School, and I hope I have made you and the School proud. I sometimes look back at my Advanced Higher project and question what on earth I was doing -- I \emph{think} this shows that I have come a long way with everything that I have learnt since 2008. I remember thinking the software I wrote back then as being so complex; it now seems so simple.

Finally, I wish to thank my supervisor, Dr. Leif Azzopardi. Leif has seen me through so much -- from my undergraduate Honours and Masters projects, and now as my PhD supervisor. His advice, wisdom, expertise and friendship have been instrumental in getting me to the stage that I could actually write this thesis up. Leif gave me so many opportunities, bestowed faith and trust in me, and provided support and encouragement when I was feeling down. I cannot express thanks enough for everything Leif has done for me. \emph{Thank you so much, Leif!} I hope we will work together again in the future.

Yes, the past four years have been an incredible journey. At times everything felt overwhelming -- like what I was doing was simply impossible. But with the love and support from everyone mentioned above, I got through it, and have managed to produce an original piece of research. With that has come a newfound confidence in myself that I will be able to achieve my future goals, whatever they may be. I think producing this thesis is testament to that, and it is something that I am very proud of.

But do you know what?

\textbf{\emph{This is just the beginning!}}

\end{preamble}

%
% \todo{====old====}
%
%
% Ian said: A PhD thesis has one name on the front. However behind this one person, who takes all the credit, are dozens of other people; cajoling, encouraging, criticising, stimulating and generally making sure that several years of alternating anguish and excitement are eventually transformed into several hundred pages of text.
%
%
% One of my friends and fellow PhD student once said to me that when the time came to write his PhD thesis, he\textbf{'}d avoid acknowledgements where the author would thank everyone and their dog for being part of their life. I on the other hand take a different light on this matter; there are a lot of people who helped me get to where I am today. To show my appreciation, \emph{I want to dedicate this work to each and every one of them.}
%
% So, where do I begin? It's been an incredible journey. Sitting at my desk on daye one -- October 1\textsuperscript{st} 2013 -- I never for one minute thought I'd drive the Pacific Motorway in New South Wales, or have a drink with good friends in Tokyo. Yet these are things that I have done, and places I have visited over the past four years. I've had the incredible good fortune to travel the world, and in doing so, meet some incredible people with whom I have shared what I have developed. As Ian Ruthven pointed out in his acknowledgements, there may be a name on the front of a PhD thesis, but countless numbers of people who were involved in the making of it.
%
% To the people in Room 221 and 220 -- my friends, Colin, Stuart, Stewart, James (or is it Andrew?), Jarana, Rami, Fajie, Fatma, Phil, Jesus, Felix, Shoki, David. Thank you all. But most of all, thank you to Hora\c{t}iu -- your friendship! Thank you to G\"{o}zel, to Frances. To Simon Rogers, to the Helen, to Gail and to Teresa, to everyone in the School who helped make my time there such an enjoyable experience. To those in the College of Science and Engineering -- especially Heather Lambie -- for allowing me to head off to undertake internships. Generally, thanks to the University of Glasgow for providing me with the opportunity to show the world what I can do, to the EPSRC for funding me, and to Rod Murray-Smith for his invaluable advice in helping me shape this thesis up. Thanks to Yashar for his wisdom and advice.
%
% Chris Johnson....
%
% Thanks to Kal J, Heikki, Jaana, Teemu and Feza for making the time I spent in Tampere so enjoyable.
%
% To Vu, Ioannis and Norbert Fuhr for the time I spent in Duisburg in November/December 2015.
%
% Thanks to Jaap Kamps for acting as my mentor at CHIIR in 2016.
%
% Thank you to Johanne and Penny for everything you did for me in Melbourne, and to Mostafa and Samira for everything you did for me in Amsterdam. Thank you to Peter, Dave and Paul for everything in Canberra at Microsoft. You all taught me so much, and equipped me to become a better scientist. To Gabrielle, James, Alan and Az for your friendship in Canberra.
%
% Thank you to everyone at the Alan Turing Institute in London for a fantastic experience. Although it didn't directly serve my PhD, I had the opportunity to work with some wonderful people -- including Emily Neilson, Prof. Terry Lyons, Hao Ni, Jeremy, Alex, Radoslaw...to name but a few.
%
% To my mother, Denise, my father, William, and my brother, Alastair -- thank you all for your unwavering support, love, and encouragement. It was tough at times, but all three of you were always there for me when I needed it. It was testing at times, but I am so happy I have managed to do you all proud. There's another doctor in the family now! To Ian Phillips -- you taught me everything I needed to know at Standard Grade and Advanced Higher. As my high school teacher, you were one of the people with the biggest influence in where I have ended up today.
%
% Finally though, I have to thank my supervisor, Dr. Leif Azzopardi. He's seen me through so much -- from my Honours project, my Masters project, and now my PhD. His advice, expertise and friendship have been instrumental in my getting to where I am today. You've given me so many opportunities, and I cannot express thanks enough in words for everything that he has done for me. Thank you, Leif.
%
% The past four years have been an incredible journey, yes. They've been tough, too. Sometimes lonely. But you know what? \emph{This is just the start.}
%
%
%
% % \begin{itemize}
% %     \item People in the office -- my friends (esp.) Hora\c{t}iu Bota, Jarana Manotumruka, Colin Wilkie, Stuart Mackie, Stewart Whiting.
% %
% %     \item Kalervo J\"{a}rvelin, Heikki Keskustalo, Jaana Kek\"{a}l\"{a}inen and Teemu P\"{a}\"{a}kk\"{o}nen for the time I spent in Tampere in September, 2014.
% %
% %     \item Vu Tran, Ioannis, Sebastien Dungs, Norbert Fuhr for the time I spent in Duisburg in November/December 2015.
% %
% %     \item Jaap Kamps as my mentor at CHIIR 2016.
% %
% %     \item Those I have met on my travels. Lucky enough to intern with Peter Bailey, Dave Hawking and Paul Thomas at the end of 2016 at Microsoft. Learnt so much there that had equipped me to be a better scientist. Johanne and Penny
% %
% %     \item Everyone at the Alan Turing Institute that made my time there enjoyable. While not directly involved in my PhD, I learnt a lot -- and
% %
% %     \item Thanks to the University -- the staff there, admin staff, etc.
% %     \item Simon Rogers, Helen Border, Teresa Bonner...
% %     \item Thanks to my funder, the EPSRC, \texttt{1367507}.
% %
% %     \item Ian Phillips!
% %
% %     \item My family, my mother, father, and brother
% %
% %     \item Finally - Leif.
% %
% % \end{itemize}
% %
% % It's been a crazy journey.
%
% \end{preamble}